---
title: "GUIDE"
author: "Marek Brynda"
date: "13 12 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs param, include=FALSE}
# ==== libraries ====
library(dplyr)
library(TH.data)
library(prodlim)
library(MASS)
library(combinat)
library(vcd)

# ==== load data ====
data("GBSG2")
```
## Data
This data frame contains the observations of 686 women:

* horTh - hormonal therapy, a factor at two levels no and yes.
* age - of the patients in years.
* menostat - menopausal status, a factor at two levels pre (premenopausal) and post (postmenopausal).
* tsize - tumor size (in mm).
* tgrade - tumor grade, a ordered factor at levels I < II < III.
* pnodes - number of positive nodes.
* progrec - progesterone receptor (in fmol).
* estrec - estrogen receptor (in fmol).
* time - recurrence free survival time (in days).
* cens - censoring indicator (0- censored, 1- event).
```{r plot Kaplan-Meier survival curves, include=T}
km0 <- prodlim(Hist(time,cens)~horTh,data=GBSG2)
## first show Kaplan-Meier without confidence limits
plot(km0,
     legend.x="bottomleft", # positition of legend
     legend.cex=0.8,
     col=c("blue","red"),
     confint=FALSE)
```
## Assign variables to proper matrices
1. X - K dimensions vector of covariates
2. Y - univariate response variable 
3. Z - treatment variable 1 ... G

```{r assign variables, include=TRUE}
Y <- GBSG2[[ncol(GBSG2)]]
Z <- GBSG2[[1]]
X <- GBSG2[2:(ncol(GBSG2)-2)]
```
